---
title: "Getting to know the data"
author: "Asem Berkalieva"
date: "4/26/2019"
output: pdf_document
---

Let's get to know the dataset:
```{r}
library(dplyr)
library(ggplot2)

# read training data (to build model)
train <- read.csv("../../Data/train_values.csv")
labels <- read.csv("../../Data/train_labels.csv")

# we will use this to assess our model
test <- read.csv("../../Data/test_values.csv")

# peek in
head(train)
head(labels)
head(test)

# general structure of the dataframe
str(train)
names(train)
```


EDA on training data:
```{r}
# distribution of cholesterol
ggplot(data = train, aes(x = serum_cholesterol_mg_per_dl)) + geom_histogram(col = "white")

# breakdown of heart disease
ggplot(data = labels, aes(x = heart_disease_present)) + geom_bar()

# merge the data
total <- merge(train, labels, by = "patient_id")

# cholesterol distribution by heart disease presence
ggplot(data = total, aes(x = serum_cholesterol_mg_per_dl)) + 
  geom_histogram(col = "white") + 
  facet_wrap(~ heart_disease_present, nrow = 2)
```


We will want to conduct SuperLearner as well as cross-validated SuperLearner on this data. 

We also need to develop the ROC curve as a measure of performance.

CV.AUC : this will give the AUC and confidence interval without us having to do the calculations





OTHER:
(1) Come up with non-parametric estimate of causal relationship
(2) Give background to the study (question we are interested in), previous findings, present the data, define the parameter of interest, etc.
(3) Where does this data come from? Who are the participants? Get to know the data & data generating process very very well..


